Blum axioms and nondeterministic computation of functions

### 2016-04-19 paper.tex
paper.tex: Rewrite last paragraph of introduction (that presents the paper).

This paper presents several attempts to establish
how a nondeterministic Turing machine could compute a function,
and to extend the concept of ``polynomial-time computable'' under each definition.
Section~\ref{sec:quality-standards} sets reasonableness criteria
to both the definition of function computation and complexity of the computation.
Section~\ref{sec:nondeterministic_computation_of_functions}
presents and criticizes the several definitions.

@@

This section surveys four approaches
for defining nondeterministic computation of functions.

@@

\subsection{Goldreich's definition}

@@

\subsection{Krentel's $\OptP$ class}

@@

\subsection{Valiant's $\#\P$ class}

@@

\section{Concluding Remarks}

@@

\section{Project Development}

>>>>

This paper presents several attempts to establish
how a nondeterministic Turing machine could compute a function,
and to extend the concept of ``polynomial-time computable'' under each definition.
Section~\ref{sec:quality-standards} sets reasonableness criteria
to both the definition of function computation and complexity of the computation.
Section~\ref{sec:nondeterministic_computation_of_functions},
which contains the several definitions,
presents and criticizes Hopcroft and Ullman's and Goldreich's definitions
(sections \ref{sec:hopcroft-ullman} and~\ref{sec:goldreich}),
proposes one possible definition that meet the quality standards
(section~\ref{sec:proposed}),
and shows other two definitions,
by Krentel (sec~\ref{sec:krentel}) and Valiant (sec~\ref{sec:valiant}),
that, altough were not proposed in the context
of general nondeterministic computation of functions,
also meet the quality standards and sidesteps the problems with the proposed definition
(mentioned in section~\ref{sec:np-completeness-extension}).
The development of this project is given in section~\ref{sec:development},
after the concluding remarks (section~\ref{sec:conclusion}).

@@

This section surveys several approaches
for defining nondeterministic computation of functions.

@@

\subsection{Goldreich's definition}
\label{sec:goldreich}

@@

\subsection{Krentel's $\OptP$ class}
\label{sec:krentel}

@@

\subsection{Valiant's $\#\P$ class}
\label{sec:valiant}

@@

\section{Concluding Remarks}
\label{sec:conclusion}

@@

\section{Project Development}
\label{sec:development}
